Open source landscape ecology tools

### 2020-10-15 paper/paper.Rmd
improves plots

ggplot_packages <- ggplot(data = r_packages_df) +
  geom_bar(aes(y = r_package_reclass, x = n_rel, fill = col), stat = "identity") + 
  # geom_text(aes(y = r_package_reclass, x = n_rel, label = label, col = col), 
  #           nudge_x = 2, size = 2.5) + 
  theme_classic(base_size = 7.5) + 
  scale_x_continuous(breaks = seq(0, 35, 5), limits = c(0, 35)) + 
  scale_fill_manual(values = c("grey50", "black")) +
  scale_colour_manual(values = c("grey50", "black")) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "Number of package mentionings [%]", y = "List the three R packages related to landscape ecology you use the most!")
```

@@

ggplot_tasks <- ggplot(data = tasks_df) +
  geom_bar(aes(y = tasks_reclass, x = n_rel, fill = col), stat = "identity") + 
  # geom_text(aes(y = tasks_reclass, x = n_rel, label = label, col = col), 
  #           nudge_x = 1.25, size = 2.5) + 
  theme_classic(base_size = 7.5) + 
  scale_x_continuous(breaks = seq(0, 20, 5), limits = c(0, 20)) + 
  scale_fill_manual(values = c("grey50", "black")) +
  scale_colour_manual(values = c("grey50", "black")) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "Number of task mentionings [%]", y = "Which are the most important tasks to your workflow?")
```

@@

```{r fig-usefulness, echo = FALSE, fig.align="center", fig.cap = "Evaluation of the usefullnes o fR for landscape ecology by the particpants of the survey. Answers were possible on a 5-point scale."}
ggplot(data = usefulness_df) +
  geom_bar(aes(x = usefulness_class, y = n_rel), 
           stat = "identity") + 
  theme_classic(base_size = 7.5) + 
  scale_y_continuous(breaks = seq(0, 60, 5), limits = c(0, 60)) + 
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "How useful do you think is R currently for landscape ecology?", 
       y = "Number of participants [%]")
```

>>>>

ggplot_packages <- ggplot(data = r_packages_df) +
  geom_bar(aes(y = r_package_reclass, x = n_rel, fill = col), stat = "identity") + 
  # geom_text(aes(y = r_package_reclass, x = n_rel, label = label, col = col), 
  #           nudge_x = 2, size = 2.5) + 
  theme_classic(base_size = 7.5) +
  theme(plot.title.position = "plot") +
  scale_x_continuous(breaks = seq(0, 35, 5), limits = c(0, 35)) + 
  scale_fill_manual(values = c("grey50", "black")) +
  scale_colour_manual(values = c("grey50", "black")) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "Number of package mentioned [%]", y = NULL,
       title = "List the three R packages related to landscape\necology you use the most")
```

@@

ggplot_tasks <- ggplot(data = tasks_df) +
  geom_bar(aes(y = tasks_reclass, x = n_rel, fill = col), stat = "identity") + 
  # geom_text(aes(y = tasks_reclass, x = n_rel, label = label, col = col), 
  #           nudge_x = 1.25, size = 2.5) + 
  theme_classic(base_size = 7.5) +
  theme(plot.title.position = "plot") +
  scale_x_continuous(breaks = seq(0, 20, 5), limits = c(0, 20)) + 
  scale_fill_manual(values = c("grey50", "black")) +
  scale_colour_manual(values = c("grey50", "black")) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "Number of task mentioned [%]", y = NULL,
       title = "Which are the most important tasks to your\nworkflow?")
```

@@

```{r fig-usefulness, echo = FALSE, fig.align="center", fig.cap = "Evaluation of the usefullnes of R for landscape ecology by the particpants of the survey. Answers were possible on a 5-point scale."}
ggplot(data = usefulness_df) +
  geom_bar(aes(x = usefulness_class, y = n_rel), 
           stat = "identity") + 
  theme_classic(base_size = 10) +
  theme(plot.title.position = "plot") +
  scale_y_continuous(breaks = seq(0, 60, 5), limits = c(0, 60)) + 
  guides(fill = FALSE, colour = FALSE) +
  labs(x = NULL,
       title = "How useful do you think is R currently for landscape ecology?", 
       y = "Number of participants [%]")
```
